---
title: "Relationship Between Traffic Noise and Energy Consumption "
output: beamer_presentation
author: "Alaina Cross, Sarah Denison, Cameryn Manley"
date: '2022-11-21'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction/Background

"Modeling urban traffic noise dependence on energy, assisted with Monte Carlo Simulation" by Rui Calejo Rodrigues

Analysis to model total energy savings using car speed (km/h), noise (dB(A)), and energy consumption (MJ)

Quantify relationship of energy reduction with car speed and noise reduction for future management of urban traffic from this perspective specifically.

Use of Monte Carlo simulation to assist with complexity of vehicle mix and uncertainty of factors of interest.

## Motivation

Analyze energy savings per deciBel - ESdB

ESdB = $\frac{\Delta energy}{\Delta noise}$

  - $\Delta energy$ - energy variation (MJ)
  
  - $\Delta noise$ - noise variation (dB)

Replicate ESdB relationship across car velocity for speeds 30-70 km/h using Monte Carlo methods and conversions of units from obtained data/resources.

Possibly explore same analysis for medium and heavy trucks and analyze differences.

## About the Data 

- Bullet 1
- Bullet 2
- Bullet 3
- Bullet 4

## Code Explanations

```{r cars, echo = TRUE}
summary(cars)
```

## Code Explanations

```{r pressure}
plot(pressure)
```

## Challenges and Potential Changes for Future

Statistical study had no access to related data, leading us to look for other data sources to use which may lead to less accuracy for replication of analysis.

## Conclusion

Able to replicate similar pattern of ESdB for car speed 30-70 km/h, but produced a smaller scale on y-axis than original study.

With noise being held constant, energy savings decreases as speed increased across interval of interest. This makes sense with energy consumption increasing as speed increases, leading to less energy being saved and ultimately decreasing ESdB.

## References



## Questions


