---
title: "Relationship Between Traffic Noise and Energy Consumption "
output: beamer_presentation
author: "Alaina Cross, Sarah Denison, Cameryn Manley"
date: '2022-11-21'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

"Modeling urban traffic noise dependence on energy, assisted with Monte Carlo Simulation" by Rui Calejo Rodrigues

Analysis to model total energy savings using car speed (km/h), noise (dB(A)), and energy consumption (MJ)

Quantify relationship of energy reduction with car speed and noise reduction for future management of urban traffic from this perspective specifically.

Use of Monte Carlo simulation to assist with complexity of vehicle mix and uncertainty of factors of interest.

## About the Data 

- Bullet 1
- Bullet 2
- Bullet 3
- Bullet 4

## Code Explanations

```{r cars, echo = TRUE}
summary(cars)
```

## Code Explanations

```{r pressure}
plot(pressure)
```

## Challenges and Potential Changes for Future


## Conclusion


## Questions


## References
